---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# recovery

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-green.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![Travis build status](https://travis-ci.org/JSzitas/recovery.svg?branch=master)](https://travis-ci.org/JSzitas/recovery)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/JSzitas/recovery?branch=master&svg=true)](https://ci.appveyor.com/project/JSzitas/recovery)
[![Codecov test coverage](https://codecov.io/gh/JSzitas/recovery/branch/master/graph/badge.svg)](https://codecov.io/gh/JSzitas/recovery?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/recovery)](https://CRAN.R-project.org/package=recovery)
[![R build status](https://github.com/JSzitas/recovery/workflows/R-CMD-check/badge.svg)](https://github.com/JSzitas/recovery/actions)
<!-- badges: end -->

## About

**recovery** is the simplest debugging tool you could wish for. It supports debugging 
the **dumb** way - running functions line by line, collecting objects, and returning the 
line which finally fails. This is somewhat inefficient, and is not advised for debugging 
computationally intensive functions. Nonetheless, for computationally unintensive tasks 
(or tasks whose computational requirements can be made reasonably small) it tends to return 
better messages than most other debugging tools. It will return, particularly, the line which 
caused the code to crash, the objects which were in scope at **that** time, and their values. 

**recovery** is dependency free and written entirely in **R**. What few other packages are used 
are used exclusively for testing and package coverage - you do not need these to make use of the 
package. 

## Examples

To start of, imagine we have a simple toy example. We are given the following function, 
which sometimes crashes: 

```{r}
some_function <- function( x = 2, y = 3, z = 2 )
{
  x <- x+y
  y <- y-z 
  z <- y+x+y
  return(z)
}
```

Now, this function seems readily simple. Now, if you supply the correct numeric arguments, 
the function will work. However, in absence of type checking, we can easily run into trouble. 
We might sometimes come across situations where things are not as they seem. Consider the following simple case: 

```{r}

what_am_i <- factor(c(1,2,3,4,5))
# this looks like an integer, right? 
what_am_i[5]

# so what happens when a user manages to call our function? 
some_function( x = 2, y = 3, z = what_am_i[5])
# that seems a bit unclear
```

We get a message about factors... but we might not notice that we are passing in a factor. 
Indeed, typically this is entirely unintentional, and happens due to type coercion, somewhere within
a different function. Sometimes this leads to errors, which is usually better. 

**recovery** to the rescue. Instead of writing your own return statements (or print statements)
as is customary during debugging, **recovery** will allow you to do approach this problem in a manner 
more befitting a programmer - lazily! 

**recovery** supports the following functions debugging functions: 
*recover - recover everything that lived inside a function environment when it crashed, 
and approximately the line **WHERE** it crashed. This still has trouble going inside certain 
scope blocks, but thanks to a return of the environment allows one to replicate the error, or repeatedly 
call recover. 
*trace_failures
*recover_types

We further intend to eventually support nested recovery - if a function within a function failed, figuring out **why** 
this happened should just be another call to **recover**. 


Document further (**TODO**)( in the meantime see documented examples within the package).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JSzitas/recovery")
```



